\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{url}


\title{
	Building a web application for student project allocation\\
	\large Bachelor Project in Computer Science}
\author{Andreas Twisttmann Askholm(aaskh20)\\{\small Advisor: Marco Chiarandini}}

\date{\today}

\begin{document}


\maketitle

\section{Subject}

Every year in the spring semester at the University of Southern Denmark, students at the Department of Mathematics and Computer Science start the work on their bachelor project. A set of project topics are made available to the students, and the students submit a prioritized list of topics they wish to work on.\\
After a set deadline the topics and the preferences of the students are fed to a piece of software that allocates projects to students using the algorithm described on pages 10-11 in ``Handling preferences in student-project allocation''\cite{Chiarandini2019}.\\
Currently the allocation software lacks a convenient interface for submitting projects and the allocation process can only be started by a single person.\\
In this project, I will build a web interface to solve these problems and a way to visualize the results of the allocation process. I will also set up a pipeline for automatic deployment of updates to the web application, with minimal downtime.

\section{Goals}

My goals for this project are to:
\begin{itemize}
	\item Set up a pipeline for automatic deployment of updates.
	\item Provide an interface where users can submit input data(e.g. project descriptions) in different forms.
	\item Allow authorized users to adjust parameters and start the allocation process.
	\item Visualize the results of the allocation process along with an explanation of this result.
\end{itemize}

\section{Tasks}

To achieve the goals of this project I will carry out the following tasks:
\begin{itemize}
	\item Identify the appropriate tools needed to build and deploy the software.
	\item Gain knowledge about the allocation software and the algorithm described in ``Handling preferences in student-project allocation''\cite{Chiarandini2019}.
	\item Build a web interface for the allocation software.
	\item Securely host the application to allow access from the internet.
	\item Implement appropriate tests for the web application. 
	\item Review the literature suggested by my advisor.
	\item Write a report describing the process and the work done.
\end{itemize}
\section{Agreement}

The software implemented within this project will be made publicly available via \url{https://git.imada.sdu.dk} under MIT license (\url{https://opensource.org/licenses/MIT}).


\bibliographystyle{plain}
\bibliography{refs}

\end{document}

